---
title: "covid 19"
author: "America Olivo"
date: "9/29/2022"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 
### This is contained in a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Question 1 - Is dying independent of sex
To find out if dying is an independent variables or not. We will be using out graphical, numerical, inferential results to get the information and percentage for the answer. 


Table of patients:
```{r}

# cross tabulation, patient state by gender

with(kRdata, table(Sex, result))

```
``` {r eval=FALSE}
kRdata <- kRdata %>%
mutate (across(where (is.character), as.factor))
```

## We create two bar charts - one based on frequency and the other on percent, use ggplot commands to do this
``` {r}
barchartGC(~result + Sex, data= kRdata)
barchartGC (~result + Sex, data=kRdata,type= "percent")
```


There were more females than males who were a part of this experiment but there were more men who died form covid. 
  
## Numerical results


## Inferential results 




## Conclusions

